Constructing the transition graphs of interacting hysterons

### 2022-05-25 Paper_draft.tex
Added figure showing examples of impossible combinations of transitions

>>>>

    \includegraphics[width=0.5\textwidth]{impossible_graphs.png}
    \caption{Examples of impossible combinations of transitions for the two-hysteron system. a) Several examples of impossible combinations of transitions. b) Example of an combination of transitions that is impossible due to a violation of the underlying base graph. c) Illustration of how the graph in (b) violates the underlying base graph.}
    \label{fig:impossiblegraphs}
